Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-02-21 coverletter.tex
update

\par
\noindent
Ana Ferreira\\
Editor \\
\textit{Geophysical Journal International}\\
~ \\
Dear Editor Ferreira,\\
\par \noindent
We are pleased to submit the original research article entitled ``Global Adjoint Tomography -- Model GLAD-M25" for publication in the \textit{Geophysical Journal International}. 
We would like to suggest the following potential 
reviewers. \\
~ \\
David Al-Attar, University of Cambridge \\
Email: da380@cam.ac.uk\\
~ \\
Heiner Igel, University of M\"unich \\
Email: igel@geophysik.uni-muenchen.de \\
~ \\
Qinya Liu, University of Toronto\\
Email:  liuqy@physics.utoronto.ca \\
~ \\
Jeroen Ritsema, University of Michigan \\
Email:  jritsema@umich.edu \\
~ \\
Carl Tape, University of Alaska Fairbanks \\
Email:  ctape@alaska.edu \\
~ \\
Jeannot Trampert, University of Utrecht \\
Email: J.A.Trampert@uu.nl \\
~ \\

>>>>

\par
\noindent
Ana Ferreira\\
Editor \\
\textit{Geophysical Journal International}\\
~ \\
Dear Editor Ferreira,\\
\par \noindent
We are pleased to submit the original research article entitled ``Global Adjoint Tomography -- Model GLAD-M25" for publication in the \textit{Geophysical Journal International}. 
I performed all the simulations on Titan, constructed the model, made all the figures and wrote the first draft before inviting the coauthors to provide edits and comments.

\par \noindent
Currently, the coauthors and I have another paper under review in the \textit{Geophysical Journal International}. The title of the paper is "Balancing Unevenly Distributed Data in Seismic Tomography: A Global Adjoint Tomography Example".

\par \noindent
We would like to suggest the following potential 
reviewers. \\
~ \\
David Al-Attar, University of Cambridge \\
Email: da380@cam.ac.uk\\
~ \\
Heiner Igel, University of M\"unich \\
Email: igel@geophysik.uni-muenchen.de \\
~ \\
Qinya Liu, University of Toronto\\
Email:  liuqy@physics.utoronto.ca \\
~ \\
Jeroen Ritsema, University of Michigan \\
Email:  jritsema@umich.edu \\
~ \\
Carl Tape, University of Alaska Fairbanks \\
Email:  ctape@alaska.edu \\
~ \\
Jeannot Trampert, University of Utrecht \\
Email: J.A.Trampert@uu.nl \\
~ \\
